A gossip-based protocol for exchanging immutable data in dynamic distributed environments

### 2011-08-10 papers/paper1/paper.tex
Added a few examples to paper.  Not sure how much more I can expand...

\section{Adam's Section}
A couple of things were hard to digest, the first of which being indirect triggers.  
It's hard to swallow the idea that you can queue an action but it's time of execution is far from guaranteed.  
The second hardest thing was simply the intimidation factor of realizing your entire summer would be working with an unknown, rather large library that nobody but the creator had used before--which was modelled after a complicated formalism I had never heard of that no one had bothered to fully develop since its inception.  
That's quite the pill to swallow.

An thing that I learned was easy was to model the automata very closely to Lynch's design.  
It was much easier for me to learn the relationship between the formalism and the code by looking at well-modelled automata, so the same would extend onto someone looking at the formalism and our code. 
Maintaining this allows for a less steep learning curve, and hopefully contributes to the automata maintaining their structural integrity as more people use the library.

In regards to building a protocol, I learned that it is extremely helpful to add and then test small bits of functionality at a time, in order to get a small working product.
Once this is complete, repeat by adding or extending the functionality.
Though this may seem trivial, calculated baby-steps made developing a protocol seem much easier than trying it all at once.

@@

>>>>

@@

\section{Adam's Section}
%% Go into more detail / provide more examples
A couple of things were hard to digest, the first of which being indirect triggers.  
It's hard to swallow the idea that you can queue an action but it's time of execution is far from guaranteed.  
The second hardest thing was simply the intimidation factor of realizing your entire summer would be working with an unknown, rather large library that nobody but the creator had used before--which was modelled after a complicated formalism I had never heard of that no one had bothered to fully develop since its inception.  
That's quite the pill to swallow.

One thing that I learned was easy was to model the automata very closely to Lynch's design.  
It was much easier for me to learn the relationship between the formalism and the code by looking at well-modelled automata, so the same would extend onto someone looking at the formalism and our code. 
Maintaining this allows for a less steep learning curve, and hopefully contributes to the automata maintaining their structural integrity as more people use the library.
An example of this would be correctly classifying input, output, and internal actions.

In regards to building a protocol, I learned that it is extremely helpful to add and then test small bits of functionality at a time, in order to get a small working product.
Once this is complete, repeat by adding or extending the functionality.
Though this may seem trivial, calculated baby-steps made developing a protocol seem much easier than trying it all at once.
For example, developing a simple transfer channel to correctly model our mftp automaton.  After this was well tested, we then moved it to transfer over multicast/broadcast.
